Collective excitations in competing phases in two and three dimensions

### 2024-01-16 paper/main.tex
home

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    In the upper panel, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behavior}
\end{figure*}

@@

@@

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
    In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behavior}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
    In the upper panels, the green markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{SC}$.
    The dashed lines represent the value found for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels.}
    \label{fig:cdw_in_sc_behavior}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{AFM}$ (blue lines) close to the corresponding phase transition $U = zV$.
    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.
    The shadings indicate the phase the system is in. Blue represents AFM while orange represents CDW.
    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
    Note the difference in the scales for the two lattices.}
    \label{fig:afm_cdw_peaks_overview}
\end{figure*}
